---
title: "HW2"
author: "William Haznaw"
date: "9/21/2021"
output: github_document
---

```{r}

library(dplyr)

# install.packages("nycflights13")
library(nycflights13)
library(ggplot2)
library(lubridate)
```



1. Find all flights that:

    Had an arrival delay of two or more hours

    Flew to Houston (IAH or HOU)
    
    Were operated by United, American, or Delta
    
    Departed in summer (July, August, and September)
    
    Arrived more than two hours late, but didn’t leave late
    
    Were delayed by at least an hour, but made up over 30 minutes in flight
    
    Departed between midnight and 6am (inclusive)
    
    
    
#### 1.1 
```{r}
filter(flights, arr_delay >= 120)

```


#### 1.4

```{r}
filter(flights, dest == "IAH" | dest == "HOU")
```

#### 1.6

```{r}
filter(flights, 
       dep_delay >= 60, 
       dep_delay - arr_delay > 30 )
```



3. How many flights have a missing dep_time? What other variables are missing? What might these rows represent?

```{r}
cancelled_flights = filter(flights, is.na(dep_time))
head(cancelled_flights)

nrow(cancelled_flights)
```


Cancelled Flights.



2. Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.

```{r}
flights <-flights %>% 
    mutate(dep_minutes_since_midnight = (dep_time %/%100)*60 + (dep_time%%100),
           arr_minutes_since_midnight = (arr_time %/%100)*60 + (arr_time%%100)) 


flights %>% 
    select(dep_minutes_since_midnight,arr_minutes_since_midnight)

    

```


Look at the number of canceled flights per day. Is there a pattern? Is the proportion of canceled flights related to the average delay? Use multiple dyplr operations, all on one line, concluding with ggplot(aes(x= ,y=)) + geom_point()

```{r} 
flights %>%
  mutate(dep_date = lubridate::make_datetime(year, month, day)) %>%
  group_by(dep_date) %>%
  summarise(cancelled = sum(is.na(dep_delay)), 
            n = n(),
            mean_dep_delay = mean(dep_delay,na.rm=TRUE),
            mean_arr_delay = mean(arr_delay,na.rm=TRUE)) %>%
    ggplot(aes(x= cancelled/n)) + 
    geom_point(aes(y=mean_dep_delay)) + 
    geom_point(aes(y=mean_arr_delay)) + 
    ylab('mean delay')





```


