---
title: "HW3"
author: "William Haznaw"
date: "10/5/2021"
output: github_document
---

html_document

```{r include=FALSE}
library(nycflights13)
library(tidyverse)
library(lubridate) 
```

Due October 5th, by midnight: In r4ds flights… What time of day should you fly if you want to avoid delays as much as possible? Does this choice depend on anything? Season? Weather? Airport? Airline? Find three patterns (“null results” are ok!). Write your results into Rmarkdown. Include a short introduction that summarizes the three results. Then, have a section for each finding. Support each finding with data summaries and visualizations. Include your code when necessary. This shouldn’t be long, but it might take some time to find the things you want to talk about and lay them out in an orderly way.

```{r message=FALSE, warning=FALSE}
flights %>%
  group_by(hour,origin) %>% 
  summarise(average_dep_delay = mean(dep_delay, na.rm = T)) %>% 
  ggplot(aes(x = hour, y = average_dep_delay)) + 
  geom_point() +
  geom_smooth()


flights %>%
  group_by(hour,origin) %>% 
  summarise(average_arr_delay = mean(arr_delay, na.rm = T)) %>% 
  ggplot(aes(x = hour, y = average_arr_delay)) + 
  geom_point() +
  geom_smooth()
```


For both arrival delays and departure delays, it appears that the earlier in the day that you fly it is more likely to have a shorter delay if any delay at all. 




**Seasons**

```{r message=FALSE, warning=FALSE}
flights2 = flights %>% 
  mutate(season = ifelse(month %in% 10:12, "Fall",
                               ifelse(month %in% 1:3, "Winter",
                                      ifelse(month %in% 4:6, "Spring",
                                             "Summer"))))

flights2 %>% 
  group_by(hour,origin,season) %>% 
  summarise(average_dep_delay = mean(dep_delay, na.rm = T)) %>% 
  ggplot(aes(x = hour, y = average_dep_delay)) + 
  geom_point() +
  geom_smooth() +
  facet_wrap(~season)

  
```

These graphs show the average departure delays of flights based on their season. While they all show a similar shape to the normal average delays in the previous graphs, 



